%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume2} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}



\name{Women in Nuclear} % Your name
\address{winatuiuc@gmail.com} % Your phone number and email

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Our Mission}
\raggedright
UIUC's Women in Nuclear (WiN) chapter is part of the
U.S. WiN's ecosystem. U.S. WiN's objectives are to
drive a culture in nuclear energy and technology
in which women and men succeed, create professional development
and networking opportunities for career advancement, and enhance understanding
and awareness of the value of nuclear energy and technology.

UIUC's WiN chapter uplifts these objectives through
providing students with a platform to participate
in activities and grow with respect to our three WiN
pillars:

\begin{enumerate}
	\item Community: To build a strong community within our chapter and
	with the Nuclear Engineering department at UIUC.
	\item Outreach: To promote the benefits of nuclear technology to the surrounding
	Urbana-Champaign community.
	\item Professional Development: To give our members support and opportunities to excel
	academically, meet professionals from industry and academia, and go beyond the classroom
	to visit nuclear-related companies/laboratories.
\end{enumerate}

\end{rSection}

\begin{rSection}{Our 2019-2020 Executive Board}
	\textbf{President:} Gwendolyn Chee  \\
	\textbf{Vice President:} Kelly Munkhtuya \\
	\textbf{Treasurer:} Sonata Valaitis \\
	\textbf{Outreach Chair:} Cassandra Soto \\
	\textbf{Professional Development Chair:} Jasmine Dinari
\end{rSection}

\begin{rSection}{Community}
	\begin{rSubsection}{Galentines Day Event}{Feb 2020}{}{}
		\item We collaborated with other Women-in organizations 
		on campus to host a Galentine's day event with food and crafts.
	\end{rSubsection}
	\begin{rSubsection}{Candy Cane Gram Sale}{Dec 2019}{}{}
		\item We sold Candy Cane Grams within the NPRE department to promote holiday spirit
		during the final stressful week of classes.
	\end{rSubsection}
	\begin{rSubsection}{Bob Ross Paint Night}{Nov 2019}{}{}
		\item We watched a Bob Ross Painting video together and each painted on a canvas. It was a very successful and fun event. 
	\end{rSubsection}
	\begin{rSubsection}{Pumpkin Patch Social}{Oct 2019}{}{}
		\item We did a fun day trip to visit a pumpkin patch.
	\end{rSubsection}
	\begin{rSubsection}{Board Game Night}{Sept 2019}{}{}
		\item A fun stress-free evening of getting to know the new WiN members.
	\end{rSubsection}
	\begin{rSubsection}{End of Semester Social with Profs}{May 2019}{}{}
		\item We hosted a fun social with the female professors in NPRE to
		give students and professors a chance to mingle in a relaxed setting.
	\end{rSubsection}
	\begin{rSubsection}{WiNning Weekend}{Apr 2019}{}{}
		\item We invited the Purdue University and Missouri Science and Technology's
		student chapters to UIUC for a weekend of fun and learning.
		During the weekend, we conducted tours of UIUC's nuclear research facilities,
		had coffee chats to discuss how each of our chapters are doing, played sports,
		and got to know each other.
	\end{rSubsection}
\end{rSection}

\begin{rSection}{Outreach}
	\begin{rSubsection}{Champaign Public Library Teen Lounge}{Feb 2020}{}{}
		\item We collaborated with the Champaign Public Library to host
		an after school session to teach middle-schoolers and high-schoolers 
		about nuclear science. 
	\end{rSubsection}
	\begin{rSubsection}{Champaign Public Library with Kids}{Jan 2020}{}{}
		\item We collaborated with the Champaign Public Library to host
		an after school session to teach elementary school kids about Nuclear 
		Technology.
	\end{rSubsection}
	\begin{rSubsection}{Nuclear Science Week 2019}{Oct 2019}{}{}
		\item We promoted nuclear technology on the quad with a
		nuclear trivia game and free cupcakes for nuclear science week.
		\item We collaborated with UIUC's ANS chapter to host a trivia night to 
		teach attendees nuclear science facts. 
		\item We collaborated with the NPRE department for a reddit Ask me anything about nuclear engineering at UIUC.
		\item We collaborated with Jensen Hughes to teach girl scouts about nuclear science for a get-to-know nuclear patch. 
	\end{rSubsection}
	\begin{rSubsection}{E-Night}{Aug 2019}{}{}
		\item We participated in Engineering Council's E-Night to promote our
		organization to incoming Engineering students.
	\end{rSubsection}
	\begin{rSubsection}{Sunflower Sale}{Apr 2019}{}{}
		\item We sold sunflowers on the quad to promote nuclear non-proliferation.
	\end{rSubsection}
	\begin{rSubsection}{Champaign Public Library}{Apr 2019}{}{}
		\item We collaborated with the Champaign Public Library to host
		an after school session to teach kids about Nuclear Technology.
	\end{rSubsection}
	\begin{rSubsection}{Engineering Open House}{Mar 2019}{}{}
		\item We participated at Engineering Open House to showcase
		the NPRE department with a nuclear fuel cycle game and nuclear trivia.
	\end{rSubsection}
	\begin{rSubsection}{Girl Scouts Stem-A-Palooza}{Nov 2018}{}{}
		\item We presented nuclear 101 to girls ages 5-11 and their parents with some demonstrations including a hand-cranked lightbulb   		and a geiger detector
	\end{rSubsection}
	\pagebreak
	\begin{rSubsection}{Urbana Central High School Visit}{Oct 2018}{}{}
		\item We went to Urbana Central High School to give a presentation
		to high school students about nuclear science.
	\end{rSubsection}
\end{rSection}

\begin{rSection}{Professional Development}
	\begin{rSubsection}{Clinton Reactor Tour}{Dec 2019}{}{}
		\item Exelon hosted us at their Clinton Reactor and gave us a
		tour of their facilities.
	\end{rSubsection}
	\begin{rSubsection}{Coffee Chats}{2018-Present}{}{}
		\item We hosted coffee chats with researchers and industry folks who
		visit our department during the school year. These have included:
		Prof Jamie Coble (University of Tennessee-Knoxville),
		Dr. Eric Loewen (GE Hitachi Nuclear Energy),
		Dr. David Chichester (Idaho National Laboratory),
		Dr. Jeffrey Favorite (Los Alamos National Laboratory),
		Dr. Francesco Venneri (Ultra Safe Nuclear),
		Prof Janalle Wharry (Purdue University),
		Dr. Glen Wurden (Los Alamos National Laboratory),
		Prof Peter Hosemann (UC Berkeley),
		and Dr. Lauren Garrison (Oak Ridge National Laboratory).
	\end{rSubsection}
	\begin{rSubsection}{Jensen Hughes Info Session}{Sept 2019}{}{}
		\item Jensen Hughes staff came to UIUC to host a info session.
	\end{rSubsection}
	\begin{rSubsection}{Curium Pharma Visit}{Feb 2019}{}{}
		\item We made a trip down to Curium Pharmaceuticals,
		a nuclear medical isotope production company in St. Louis.
	\end{rSubsection}
	\begin{rSubsection}{LaSalle Reactor Tour}{Nov 2018}{}{}
		\item Exelon hosted us at their LaSalle Reactor and gave us a
		tour of their facilities.
	\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------

\end{document}
